---
title: "Lab 3 Report"
author: "Beau Ayers"
date: "`r format(Sys.Date())`"
output: github_document
---

Instructions for this lab report can be found on [Your assignment section of Lab Assignment 3 Introduction to ggplot2](https://biol275-msum.github.io/introduction-to-ggplot2.html#your-assignment) on the lab website.

## Fireflies

> A. Insert an R code chunk and create a graph depicting the frequency distribution of the 35 mass measurements. It should have legible text and appropriate axis labels.

```{r}
library(tidyverse)

firefly_data <- read_csv("https://whitlockschluter.zoology.ubc.ca/wp-content/data/chapter02/chap02q19FireflySpermatophoreMass.csv")

firefly_data
# A tibble: 35 x 1
#> spermatophoreMass
#> <dbl>
#> 1             0.047
#> 2             0.037
#> 3             0.041
#> 4             0.045
#> 5             0.039
#> 6             0.064
#> 7             0.064
#> 8             0.065
#> 9             0.079
#> 10             0.07 
# ... with 25 more rows

ggplot(data = firefly_data) +
  geom_histogram(mapping = aes(x = spermatophoreMass), binwidth = 0.005,
                 fill = "#C5351B", color = "black") +
  labs(x = "Mass of Spermatophore (mg)", y = "Frequency (number of fireflies)") +
  theme_classic() +
  theme(
    axis.title = element_text(face = "bold"),
    axis.text = element_text(color = "black", size = rel(1))
  )
```


> B. What type of graph did you choose in part (A)? Why?

I chose a histogram. My reasoning for this is the data is numerical not categorical.

> C. Describe the shape of the frequency distribution. What are its main features?

The graph is skewed to the right.

> D. What term would be used to describe the largest measurement in the frequency distribution? You can refer to the lecture slides, your notes, or the textbook.

The highest point or measurement would be the mode of the graph.

## Bird orders

I read the data using the code provided by the instructor. The dataset is from the auk package and was originally named ebird_taxonomy. I converted it to a tibble, removed non-species taxa, and named the new dataset birds.

```{r}
library(auk)                          # load the auk package
birds <- ebird_taxonomy %>%           # start with the ebird_taxonomy data
  as_tibble() %>%                     # tibbles print better in the console
  filter(category == "species")       # remove non-species taxa
```

> E. How many bird species are in the new birds dataset? How did you find out?

10721. There are 10721 rows.

> H. How many orders are there? You can get this right by counting on the graph, but you will only get full points if you use some code to figure it out.

41 different Orders.
```{r}
nrow(distinct(birds, order))
```


> F. Insert an R code chunk and create a graph depicting the distribution of orders in the birds dataset. Sort the orders with the most frequent on the left. It should have legible text and appropriate axis labels.

```{r}
library(auk)                          # load the auk package
birds <- ebird_taxonomy %>%           # start with the ebird_taxonomy data
  as_tibble() %>%                     # tibbles print better in the console
  filter(category == "species")       # remove non-species taxa

ggplot(data = birds) +
  geom_bar(mapping = aes(x = fct_infreq(order)), fill = "#C5351B") + 
  labs(x = "Order", y = "Frequency (number of birds)", 
       title = "Number of Birds in an Order") +
  scale_y_continuous(limits = c(0, 7000), expand = expansion(mult = 0)) +
  theme_classic(base_size = 12) +
  theme(
    axis.title = element_text(face = "bold"),
    axis.text = element_text(color = "black", size = rel(1)),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.ticks.x = element_blank()
  )
```


> G. What kind of graph did you create? Why?

I created a Bar Graph because the data in this section was categorical.

## Links to peer review

I reviewed MaryJo's lab report at this URL: https://github.com/BIOL275-MSUM/lab-3-intro-to-ggplot-MaryJo-Nelson


MaryJo reviewed my lab report at this URL: https://github.com/BIOL275-MSUM/lab-3-intro-to-ggplot-BeauAyers

## Session Info

Here is my session information:

```{r}
sessioninfo::session_info()
```
